Typing a linear \picalc

### 2020-04-10 paper/paper.tex
More ergonomic types, get closer to subst input

\subsection{Typing with Leftovers}
\label{leftover typing}

@@

    \inferrule
    {chan_i : \contains{\gamma}{\Gamma}{i}{\channel{t}{x}}{\li}{\Xi} \\\\
     cont : \types{\gamma \comma t}{\Xi \comma x}{P}{\Theta \comma \lz}}
    {\constr{recv} \; chan_i \; cont : \types{\gamma}{\Gamma}{\recv{i}{P}}{\Theta}}

    \inferrule
    {chan_i : \contains{\gamma}{\Gamma}{i}{\channel{t}{x}}{\lo}{\Delta} \\\\
     loc_j : \contains{\gamma}{\Delta}{j}{t}{x}{\Xi} \\\\
     cont : \types{\gamma}{\Xi}{P}{\Theta}}
    {\constr{send} \; chan_i \; loc_j \; cont : \types{\gamma}{\Gamma}{\send{i}{j}P}{\Theta}}

>>>>

\subsection{Typing with Leftovers}
\label{leftover-typing}

@@

    \inferrule
        {\stacked{
            chan_i : \contains{\gamma}{\Gamma}{i}{\channel{t}{x}}{\li}{\Xi} \\\\
            cont \hspace{0.6em} : \types{\gamma \comma t}{\Xi \comma x}{P}{\Theta \comma \lz}}}
        {\constr{recv} \; chan_i \; cont : \types{\gamma}{\Gamma}{\recv{i}{P}}{\Theta}}

    \inferrule
        {\stacked{
            chan_i : \contains{\gamma}{\Gamma}{i}{\channel{t}{x}}{\lo}{\Delta} \\\\
            loc_j \hspace{0.8em} : \contains{\gamma}{\Delta}{j}{t}{x\hspace{4em}}{\Xi} \\\\
            cont \hspace{0.6em} : \types{\gamma}{\Xi}{P\hspace{6em}}{\Theta}}}
        {\constr{send} \; chan_i \; loc_j \; cont : \types{\gamma}{\Gamma}{\send{i}{j}P}{\Theta}}
